Windowed least-squares model reduction for dynamical systems

### 2019-10-16 section4/spatial_numerical.tex
add linear/nonlinear comment

where $\stateFOMDiscreteArg{n,i} \approx \stateFOMArg{}{\timeWindowArg{n}{i}} \in \RR{\fomdim}$ is the discrete approximation to the FOM state at the $i$th time instance over the $n$th window and $\residLMSArg{n,i}$ is the discrete linear multistep residual over the $i$th time instance of the $n$th window and is defined as

@@

Additionally, $\Delta t^{n,i} = \timeWindowArg{n}{i} - \timeWindowArg{n}{i-1}$ is the time step, $\lmsWidthArg{n}{i}$ is the width of the multistep scheme at the $i$th time instance over the $n$th window, and $\alpha^{n,i}_j$ and $\beta^{n,i}_j$ are coefficients that 
define the specific type of multistep scheme. Examples of linear multistep schemes include Adams--Bashforth schemes and  
Adams--Moulton schemes. 

@@

For notational simplicity, we assume the linear multistep method employs time instances from only within the current time window. In general, the linear multistep method at the $n$th window could be designed to employ multiple time instances from previous time windows.

@@

\methodAcronym\ sequentially computes the approximate solutions $\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}}$, $n=1,\ldots,\nslabs$, as the solution to the minimization problem

@@

&\underset{\stateyDiscreteArgnt{0},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}} \in \trialspace}{\text{minimize } }

@@

Defining $\genstateDiscreteArg{n,i} \in \RR{\romdim}$ to be the discrete approximation to the generalized coordinates at the $i$th time instance over the $n$th window, 
the minimization problem can be written equivalently as

@@

& \underset{\genstateyDiscreteArg{0},\ldots,\genstateyDiscreteArg{\nstepsArg{n}}}{\text{minimize } }

@@

The optimization problem takes the form of a \textit{weighted (non)linear least-squares problem}, 
in where the weights correspond the quadrature weights.  
Before proceeding, it is worth mentioning that~\eqref{eq:obj_gen_lms_final} corresponds to a least-squares problem due
to the reduction in \textit{spatial} complexity, as opposed to the reduction
in temporal complexity (the same  number of temporal constraints and temporal 
degrees of freedom have been introduced).

@@

\begin{remark}
For the limiting case where $\nstepsArg{n} = 1$ such that the window size is equivalent to the time step, $\DeltaSlabArg{n} \equiv \timeWindowArg{n}{1} - \timeWindowArg{n}{0}$, and uniform 
quadrature weights are used, \methodAcronym\ with \spatialAcronym\ trial subspaces solved via the direct approach recovers LSPG.
\end{remark} 
\subsubsection{Solution to the least-squares problem through the Gauss--Newton method}
Discretization through linear multistep methods (as well as other techniques) 
results in a (non)linear least-squares problem.
A variety of algorithms exist for solving least-squares problems, including trust region approaches, the Gauss–Newton method, and the Levenberg–Marquardt method.  
The numerical experiments presented in this work consider the Gauss--Newton method, and as such we outline this approach here.

>>>>

where $\stateFOMDiscreteArg{n,i} (\approx
\stateFOMArg{}{\timeWindowArg{n}{i}})
\in \RR{\fomdim}$ and $\residLMSArg{n,i}$ denotes the FOM O$\Delta$E
residual over the $i$th time instance of the $n$th window 
defined as

@@

Here, $\Delta t^{n,i} \defeq \timeWindowArg{n}{i} - \timeWindowArg{n}{i-1}$
denotes the time step, $\lmsWidthArg{n}{i}$ denotes the number of time steps employed by the scheme at the $i$th time instance over the $n$th window, and
$\alpha^{n,i}_j,\beta^{n,i}_j\in\RR{}$ denote coefficients that 
define the specific type of multistep scheme. 

@@

For notational simplicity, we assume the linear multistep method employs time
	instances from only within the current time window. In general, the linear
	multistep method at the $n$th window could be designed to employ multiple
	time instances from previous time windows. \KTC{What are the implications of
	this? I suggest removing this and adding a simple condition, maybe with a
	footnote.}

@@

\KTC{Don't these weights need to be non-negative to guarantee the integral is
non-negative? If so, then specify $\quadWeightsLMSScalarArg{n}{i} \in\RR{}_+$}
\methodAcronym\ sequentially computes the solutions
$\approxstateDiscreteArg{n,0},\ldots,\approxstateDiscreteArg{n,\nstepsArg{n}}$,
$n=1,\ldots,\nslabs$ that satisfy
	\KTC{What is $\genstate^{n-1}(\timeEndArg{n-1} ) $ doing here? Two problems
	(1) there is no notion of a generalized coordinate $\genstate$ yet, and (2)
	this should be the discrete solution, not the exact solution evaluated at
	the final time.}

@@

	&\underset{(\stateyDiscreteArgnt{0},\ldots,\stateyDiscreteArgnt{\nstepsArg{n}}) \in \trialspace\otimes \RR{\lmsWidthArg{n}{i}+1}}{\text{minimize } }

@@

	Equivalently, WLS sequentially computes the generalized
	coordinates
	$\genstateDiscreteArg{n,0},\ldots,\genstateDiscreteArg{n,\timeWindowArg{n}{i}}$,
	$n=1,\ldots,\nslabs$ 
with $\genstateDiscreteArg{n,i}(\approx
	\genstateArgnt{n}(\timeWindowArg{n}{i}))\in\RR{\romdim}$
	that satisfy

@@

	&
	\underset{(\genstateyDiscreteArg{0},\ldots,\genstateyDiscreteArg{\nstepsArg{n}})\in\RR{\romdim}\otimes \RR{\lmsWidthArg{n}{i}+1}}{\text{minimize } }

@@

The optimization problem takes the form of a \textit{weighted least-squares
	problem}. \KTC{I got rid of (non)linear. If it's either linear or nonlinear,
	then omit it as an adjective, as this is no longer descriptive. }
We emphasize that optimization problem~\eqref{eq:obj_gen_lms_final} associates
	with an \spatialAcronym\ trial subspace characterized by a reduction in
	spatial complexity, but no reduction in temporal complexity.

@@

\begin{remark}
For the limiting case where $\nstepsArg{n} = 1$ such that the window size is equivalent to the time step, $\DeltaSlabArg{n} \equiv \timeWindowArg{n}{1} - \timeWindowArg{n}{0}$, and uniform 
quadrature weights are used, \methodAcronym\ with \spatialAcronym\ trial
	subspaces solved via the direct approach recovers LSPG. \KTC{Not exactly. To
	make this LSPG as presented earlier, also require the time grid here to
	align with the time grid used for time integration earlier. Also, this
	formulation requires allowing the stencil to go back to time steps at
	previous windows.} 
\end{remark} 
\subsubsection{Solution to the least-squares problem through the Gauss--Newton method}
	\KTC{If the dynamics are linear, doesn't this just yield a linear
	least-squares problem that can be solved directly? We need to present this
	more clearly.}
Discretization through linear multistep methods (as well as other techniques) 
results in a (non)linear least-squares problem.
A variety of algorithms exist for solving least-squares problems, including trust region approaches, the Gauss–Newton method, and the Levenberg–Marquardt method.  
The numerical experiments presented in this work consider the Gauss--Newton method, and as such we outline this approach here.
